\MakeUppercase{Linear versus centred Colouring Numbers}\thanks{This research was partly funded by NSERC.}

### 2022-04-05 lin-vs-cen.tex
Pfffft

For a  bipartite graph $H$, the two parts of $V(H)$ are denoted by $L(H)$ and $R(H)$ and we use the convention that an edge $vw$ has $v\in L(H)$ and $w\in R(H)$.  A \defin{matching} $M$ in a bipartite graph $H$ is a subgraph of $H$ in which each vertex has degree at most $M$.  We say that $M$ \defin{saturates} a set $S\subseteq V(H)$ if $\deg_M(v)=1$ for each $v\in S$.  We make use of Hall's Famous Marriage Theorem (see, for example \citet[Theorem~2.1.2]{diestel:graph}):

\begin{lem}\label{hall}
  Let $H$ be a bipartite graph with the property that $|N_H(A)|\ge |A|$ for each $A\subseteq L(H)$.  Then $H$ contains a matching that saturates $L(H)$.
\end{lem}

More specifically, we make use of the following (polygamous) generalisation of \cref{hall}, which follows from \cref{hall} by replacing each vertex $x\in L(H)$ with $d$ vertices $x_1,\ldots,x_d$ each having the same neighbourhood as $x$.  More precisely, we apply \cref{hall} on the graph $H':=H-\{x\}\cup\{x_iy:i\in\{1,\ldots,d\},\, y\in N_H(x)\}$.

\begin{cor}\label{d_hall}
  Let $d\ge 1$ be an integer and let $H$ be a bipartite graph with the property that $|N_H(A)|\ge d|A|$ for each $A\subseteq L(H)$.  Then $H$ contains a subgraph $M$ such that $\deg_M(v)=d$ for each $v\in L(H)$ and $\deg_M(w)\le 1$ for each $y\in R(H)$.
\end{cor}

@@

  Taking $\tau = 450(20r+1)^4+1$, and using \cref{weight_product,probability}, we find that
  \[
     \Pr\left(E_\alpha\right) \le w(E_\alpha)\prod_{\beta\in\Gamma_\alpha}(1-w(\Gamma_\alpha))
  \]
  provided that 
  \[   |\Phi_\alpha| \ge 150(20r+1)^2\left(\log\left(450(20r+1)^4+1\right) + 6(2r+1)^2(1+\log(2|\Phi_\alpha|)) \right) \enspace .
  \]
  The right hand side of this last equation is of the form $O(r^4\log|\Phi_\alpha|)$.  Since $|\Phi_\alpha|\ge d$, this can therefore be satisfied for some $d\in O(r^4)$.

>>>>

For a  bipartite graph $H$, the two parts of $V(H)$ are denoted by $L(H)$ and $R(H)$ and we use the convention of writing an edge $xy$ so that its first endpoint $x$ is in $L(H)$ and its second endpoint $y$ is in $R(H)$.  A \defin{matching} $M$ in a bipartite graph $H$ is a subgraph of $H$ in which each vertex has degree at most $M$.  We say that $M$ \defin{saturates} a set $S\subseteq V(H)$ if $\deg_M(v)=1$ for each $v\in S$.  We make use of (the difficult half of) Hall's Marriage Theorem (see, for example \citet[Theorem~2.1.2]{diestel:graph}):

\begin{thm}[\citet{hall:on}]\label{hall}
  Let $H$ be a bipartite graph with the property that $|N_H(A)|\ge |A|$ for each $A\subseteq L(H)$.  Then $H$ contains a matching that saturates $L(H)$.
\end{thm}

More specifically, we make use of the following (polygamous) version of the Marriage Theorem, which is obtained by replacing each vertex $x\in L(H)$ with $d$ vertices $x_1,\ldots,x_d$ each having the same neighbourhood as $x$.  More precisely, we apply \cref{hall} on the graph $H':=H-\{x\}\cup\{x_iy:i\in\{1,\ldots,d\},\, y\in N_H(x)\}$.

\begin{cor}\label{d_hall}
  Let $d\ge 1$ be an integer and let $H$ be a bipartite graph with the property that $|N_H(A)|\ge d|A|$ for each $A\subseteq L(H)$.  Then $H$ contains a subgraph $M$ such that $\deg_M(v)=d$ for each $x\in L(H)$ and $\deg_M(y)\le 1$ for each $y\in R(H)$.
\end{cor}

@@

  Comparing \cref{weight_product,probability} we see that both quantities decrease exponentially in $|\Phi_\alpha|$ but \cref{weight_product} does so at a rate that can be controlled with $\tau$.
  Taking $\tau = 450(20r+1)^4+1$, and using \cref{weight_product,probability}, we find that
  \[
     \Pr\left(E_\alpha\right) \le w(E_\alpha)\prod_{\beta\in\Gamma_\alpha}(1-w(\Gamma_\alpha))
  \]
  provided that 
  \[   |\Phi_\alpha| \ge 150(20r+1)^2\left(\log\left(450(20r+1)^4+1\right) + 6(2r+1)^2(1+\log(2|\Phi_\alpha|)) \right) \enspace .
  \]
  The right hand side of this last equation is of the form $O(r^4\log|\Phi_\alpha|)$.  Since $|\Phi_\alpha|\ge d$, this can therefore be satisfied for some $d\in O(r^4)$.
